\Title

### 2021-06-28 manuscript/content.tex
Review source layouts section of the methods
Nothing major, just some wording
Review the source layouts results section

We have used synthetic gravity datasets to test the interpolation accuracy of
the difference horizontal and vertical source distribution strategies as well
as the gradient-boosted equivalent source method.
To generate the data, we created a model that is made out of \NPrisms{}
right-rectangular prisms, distributed on a region of
\ModelEasting{}$\times$\ModelNorthing{} with depths varying between
\ModelDepth{} and zero.
The density contrast of prisms ranges from \ModelMinDensity{} to
\ModelMaxDensity{}.
The model includes prisms of different shapes, sizes, and depths to create
gravity disturbances with a variety of wavelengths.

We created two synthetic datasets from the model, one simulating a ground
survey and another an airborne acquisition (Fig.~\ref{fig:synthetic-layouts}).
To create the synthetic ground survey, we selected measurement positions from a
portion of a public domain dataset for Southern Africa, available through the
NOAA National Centers for Environmental Information (NCEI).
For the synthetic airborne survey, we used a portion of the Great Britain
Aeromagnetic Survey acquired by Hunting Geology and Geophysics Ltd and Canadian
Aeroservices Ltd between 1955 and 1965 and made publicly available by the
British Geological Survey (BGS).
In both cases, we rescaled the horizontal coordinates of each survey portion to
span an area of \SurveyEasting{}$\times$\SurveyNorthing{}, matching the model
dimensions.
The ground survey contains \GroundSurveyPoints{} observations distributed at
heights between \GroundSurveyMinHeight{} and \GroundSurveyMaxHeight{}
(Fig.~\ref{fig:synthetic-layouts}a).
The airborne survey has \AirborneSurveyPoints{} observations at heights between
\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}
(Fig.~\ref{fig:synthetic-layouts}c).

@@

We investigated the effect of different strategies for distributing the
equivalent sources horizontally and vertically on interpolation accuracy.
To do this, we used the damped least-squares solution described in
Section~\ref{sec:eql_inversion} (without gradient boosting) to interpolate the
synthetic datasets (Fig.~\ref{fig:synthetic-layouts}) and compared the results
against the target grid (Fig.~\ref{fig:synthetic-target}).
This process was repeated for each combination of horizontal layout
(\emph{sources below data} and \emph{block-averaged sources}) and depth type
(\emph{constant}, \emph{relative}, and \emph{variable}) and for regular grid
sources with a constant depth, totalling 7 different combinations.

>>>>

We have used synthetic gravity datasets to test the interpolation accuracy of
the difference horizontal and vertical source distribution strategies as well
as the gradient-boosted equivalent sources method.
To generate the data, we created a model of \NPrisms{} right-rectangular
prisms,
distributed in a \ModelEasting{}$\times$\ModelNorthing{} area with depths
varying between \ModelDepth{} and zero.
The density contrast of prisms ranges from \ModelMinDensity{} to
\ModelMaxDensity{}.
The model includes prisms of different shapes, sizes, and depths to create
gravity disturbances with a variety of wavelengths.

We created two synthetic datasets from the model, one simulating a ground
survey and another an airborne acquisition (Fig.~\ref{fig:synthetic-layouts}).
To create the synthetic ground survey, we selected measurement positions from a
portion of a public domain gravity dataset for Southern Africa, available
through the NOAA National Centers for Environmental Information (NCEI).
For the synthetic airborne survey, we used a portion of the Great Britain
Aeromagnetic Survey acquired by Hunting Geology and Geophysics Ltd and Canadian
Aeroservices Ltd between 1955 and 1965 and made publicly available by the
British Geological Survey (BGS).
In both cases, we rescaled the horizontal coordinates of each survey portion to
span an area of \SurveyEasting{}$\times$\SurveyNorthing{}, matching the model
dimensions.
The ground survey contains \GroundSurveyPoints{} observations distributed at
heights between \GroundSurveyMinHeight{} and \GroundSurveyMaxHeight{}
(Fig.~\ref{fig:synthetic-layouts}a).
The airborne survey has \AirborneSurveyPoints{} observations at heights between
\AirborneSurveyMinHeight{} and \AirborneSurveyMaxHeight{}
(Fig.~\ref{fig:synthetic-layouts}c).

@@

We investigated the effect on interpolation accuracy of different strategies
for distributing the equivalent sources horizontally and vertically.
To do this, we used the damped least-squares solution described in
Section~\ref{sec:eql_inversion} (without gradient boosting) to interpolate the
synthetic datasets (Fig.~\ref{fig:synthetic-layouts}) and compared the results
against the target grid (Fig.~\ref{fig:synthetic-target}).
This process was repeated for each combination of horizontal layout
(\emph{sources below data} and \emph{block-averaged sources}) and depth type
(\emph{constant}, \emph{relative}, and \emph{variable}) and for regular grid
sources with a constant depth, totalling 7 different combinations.
